### 2016-11-06 Paper_v1.tex
Nov6_3

\subsection*{Global and local sensitivity analysis}
We conducted a global sensitivity analysis, using the variance-based method of Sobol, to estimate which of the experimentally controllable parameters affected the performance of the reduced order model \citep{SOBOL_METHOD}.
This included the initial conditions of glucose, oxygen, amino acids, and enzymes.
We computed the total sensitivity index of each parameter relative to a performance objective of area under the CAT curve (CAT production).
We established the sampling bounds for each parameter from the value of that parameter in the set used to generate the ensemble.
We used the sampling method of Saltelli \textit{et al.} \citep{Saltelli:2010} to compute a family of $N\left(2d+2\right)$ sets which obeyed our parameter ranges,
where $N$ was the number of trials, and $d$ was the number of parameters in the model. In our case, $N$ = 300 and $d$ = 185, so the total sensitivity indices were computed from
111,600 model evaluations. The variance-based sensitivity analysis was conducted using the SALib module encoded in the Python programming language \citep{SALIB}.
We conducted a local sensitivity analysis to estimate which of the other model parameters affected performance.
This included the same parameters that were varied in the ensemble: rate constants, saturation constants, and control parameters.
The local sensitivity for each parameter was calculated across a sub-ensemble of 180 parameter sets, randomly chosen from the ensemble of 18,000 sets:
\begin{equation}\label{eqn:local-sensitivity}
\begin{split}
    S_{ij}=\frac{p_{ij}}{AUC(p_{ij})}\frac{AUC(p_{ij}+\Delta p_{ij})-AUC(p_{ij})}{\Delta p_{ij}}\qquad{i=1,2,\hdots,\mathcal{E}}\qquad{j=1,2,\hdots,\mathcal{P}} \\
    \Delta p_{ij}=0.001\;p_{ij}\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
\end{split}
\end{equation}
where $\mathcal{E}$ denotes the number of parameter sets in the sub-ensemble, equal to 180, $\mathcal{P}$ denotes the number of parameters, equal to 652, $S_{ij}$ denotes the sensitivity of the $j$th parameter for the $i$th parameter set, $p_{ij}$ denotes the value of the $j$th parameter for the $i$th parameter set, $\Delta p_{ij}$ denotes the perturbation of the $j$th parameter for the $i$th parameter set, equal to 0.1\% of the parameter value, and $AUC()$ denotes the area under the CAT curve.
We then calculated the mean and standard error of each local sensitivity across the sub-ensemble of 180 sets.

>>>>

\subsection*{Local sensitivity analysis}
We determined the reactions most important to protein production by computing the local sensitivity of CAT concentration to each rate constant in the network.
Each sensitivity index was formulated as:
\begin{equation}\label{eqn:local-sensitivity}
\begin{split}
    S_{ij}=norm(CAT(p_i,p_j,t)-CAT(\alpha*p_i,\alpha*p_j,t))\qquad{i,j=1,2,\hdots\mathcal{P}}\\
\end{split}
\end{equation}
where $S_{ij}$ denotes the sensitivity of CAT production to the $i$th and $j$th parameters, $CAT(p_i,p_j,t)$ denotes CAT concentration as a function of time and the $i$th and $j$th parameters, $\alpha$ denotes the perturbation factor, equal to 1.01, and $\mathcal{P}$ denotes the number of rate constants, equal to 163.
In calculating the pairwise sensitivities, each parameter was perturbed by 1\%;
